%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Samson Olusegun} \\[7.5pt]
\textbf{Software Engineer} \\[10pt]
\normalsize{\textit{Experience Summary}: A results-driven Software Engineer with a proven track record in translating business needs into efficient technical solutions. Specializes in Typescript, Rust, Python, and Cloud Development, with a keen interest in Bitcoin. Committed to continuous learning and innovation, actively engaged in both tech, and non-tech communities. Passionate about mentoring and fostering growth.} \\[10pt]
\href{https://linkedin.com/in/samson-olusegun}{\raisebox{-0.04\height}\faLinkedin\ Samson-Olusegun} \  $|$ \
\href{https://twitter.com/nully0x}{\raisebox{-0.04\height}\faTwitter\ nully0x} \ $|$ \  
\href{https://github.com/nully0x}{\raisebox{-0.04\height}\faGithub\ nully0x} \ $|$ \
\href{https://www.nully0x.xyz}{\raisebox{-0.04\height}\faGlobe\ nully0x.xyz} \ $|$ \
\href{mailto:nully0x@proton.me}{\raisebox{-0.04\height}\faEnvelope\ nully0x@proton.me} \ $|$ \
\href{tel:+2349160918616}{\raisebox{-0.04\height}\faMobile\ +2349160918616}
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

\section{TECHNICAL EXPERIENCE}

\begin{joblong}{Mavapay Digital Solutions, US -- Software Engineer (Remote)}{Dec 2024 -- Present}
\item Architect and manage scalable backend infrastructure, ensuring high availability and performance for payments systems.
\item Implement proactive monitoring, alerting, and incident response processes, reducing downtime by 30\%.
\item Optimize cloud servers, networks, and databases to achieve cost savings and improved system reliability.
\item Collaborate with CTO to design secure, high-performance backend architecture and product roadmaps.
\item Develop backend systems on the Bitcoin protocol, enabling seamless crypto-based transactions.
\end{joblong}

\begin{joblong}{Chaincode Labs, US -- Open Source Developer (Remote)}{Mar 2023 -- Dec 2024}
\item Engineered and maintained backend infrastructure for Bitcoin Dev Project platform, improving query response times by 40\%.
\item Designed and built a transcript review system for knowledge based applications, increasing engagement and usability for bitcoin developers.
\item Built cost-efficient deployment pipelines, reducing release time and improving reliability.
\item Integrated Lightning Network features (L402, sat rewards) to enhance micropayment processing.
\end{joblong}

\begin{joblong}{Kernel Systems, Nigeria -- Technical Lead (Remote, Part-Time)}{Oct 2022 -- Present}
\item Led backend architecture design and code reviews, ensuring engineering best practices and maintainability.
\item Delivered Bitcoin-powered payroll infrastructure supporting multi-currency settlements.
\item Automated deployment pipelines to streamline release cycles and reduce operational overhead.
\end{joblong}

\begin{joblong}{Helgg, Nigeria -- Lead Backend Engineer (Remote, Part-Time)}{Aug 2022 -- May 2023}
\item Built IoT-enabled e-scooter mobility backend systems, enabling real-time fleet monitoring.
\item Defined API standards, CI/CD workflows, and infrastructure-as-code practices for engineering teams.
\item Reduced operational issues through robust error handling and observability tooling.
\end{joblong}

\begin{joblong}{Qala Dev, Nigeria -- Bitcoin Protocol Developer Intern (Remote)}{Jan 2021 -- Jul 2021}
\item Researched Bitcoin and Lightning protocols; contributed to open-source Bitcoin development projects.
\item Implemented Bitcoin testnet experiments and supported hackathons to improve Lightning adoption.
\end{joblong}

\begin{joblong}{Adekunle Ajasin University, Nigeria -- Web Developer}{Jan 2021 -- Jun 2021}
\item Developed student portal web applications to automated student request across departments.
\item Conducted QA testing and bug resolution, reducing student service downtime.
\item Collaborated closely with the lead web developer, ensuring rigorous testing and quality assurance of web applications.
\end{joblong}

\section{OTHER EXPERIENCE}

\begin{joblong}{Propel, Germany -- Technical Jury (Remote)}{Nov 2022 -- Jan 2024}
\item Conducted 200+ technical interviews, improving candidate quality scores by 15\% for client acceptance.
\item Standardized evaluation frameworks, cutting review cycles by 20\%.
\end{joblong}

\begin{joblong}{Tech4Dev, Nigeria -- Frontend Development Consultant (Contract)}{Aug 2022 -- Jun 2023}
\item Designed and delivered a modern frontend engineering curriculum for 200+ trainees.
\item Created training resources and assessments that boosted trainee graduation rates.
\end{joblong}


\section{EDUCATION}

\begin{tabularx}{\linewidth}{@{}l X@{}}
Adekunle Ajasin University & \textbf{Bachelor of Science in Economics} \\
                          & December 2015 - April 2021 \\[10pt]
\end{tabularx}

\section{SKILLS}

\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming} & HTML / CSS / Javascript Typescript / Python / Rust / Bitcoin Script / Zig \\
\textbf{Concepts} & Design Implementation / Test-Driven Development / Microservices / Monolithics \\
\textbf{Web Frameworks} & Angular / NodeJs / AdonisJs / Express / Actix / Svelte / Axum \\
\textbf{Database} & MySQL / Firestore / MongoDB / PostgreSQL / DynamoDB \\
\textbf{Tools} & Git / PowerApps / Docker / TravisCI / Kubernetes / Terraform / Github Actions / Ansible / Pulumi  \\
\textbf{Data Processing} & Google Colab / Google Data Lab / Azure Data Studio / Microsoft Power BI / Eviews / SPSS / Excel \\
\textbf{Cloud} & Google Cloud Platform / Azure / AWS / Heroku / Oracle Cloud
\end{tabularx}

\section{INTEREST}
Data / Bitcoin / Movies / Traveling

\section{LANGUAGES}
English / Yoruba / French (Beginner)

\section{PROJECTS}

\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Serverless Veeds} & \hfill \href{https://github.com/nully0x/serverless-veeds}{Github} \\
& Developed to illustrate video sharing using serverless architecture within GCP ecosystem\\[10pt]
\textbf{Tweet Annotator Helpers} & \hfill \href{https://github-gist.com}{github-gist} \\
& Developed to annotate and classify text (tweets) extracts using Twitter API, to further subject to sentiment analysis. \\[10pt]
\textbf{Udagram} & \hfill \href{https://github.com}{github} \\
& An image-sharing web app. Implementing a set of resources on the AWS cloud environment using various stacks such as Kubernetes, RDS, S3, Cloudformation, Amplify, Docker, Nodejs and Ionic/Angular
\end{tabularx}

\section{CERTIFICATE}
\textbf{Cloud Developer Nanodegree} - Udacity

\vfill
\center{\footnotesize Last updated: \today}

\end{document}